Joint analysis of read count data

### 2020-09-11 combined_analysis/combine_all_DLPFC.Rmd
Inital commit

# # HBCC - sgACC
# counts.HBCC4 = fread(synGet('syn21867866')$path, data.table=FALSE)
# rownames(counts.HBCC4) = counts.HBCC4$Geneid
# counts.HBCC4 = counts.HBCC4[,-c(1:6)]

>>>>

# # HBCC - sgACC
counts.HBCC4 = fread(synGet('syn21867866')$path, data.table=FALSE)
rownames(counts.HBCC4) = counts.HBCC4$Geneid
counts.HBCC4 = counts.HBCC4[,-c(1:6)]
